\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Problem Set 1}
\author{William Townsend}

\begin{document}
\maketitle


\section{}

I created an account on Github.com and starred our class repository. I also added a photo of me in my profile.



\section{}

I forked the class repository to my own account. I also went to settings and clicked on collaborators. From there I entered my GitHub username.

\section{}

I downloaded PuTTY, FileZilla, git, and R. I also linked git to RStudio.

\section{}

For this document I used overleaf.com.

\section{}

I am taking this class to better comprehend manipulating large data sets. In addition, I hope to gain a better understanding of statistical coding in RStudio and other important software programs. As a second year PhD student at OU, I believe my comparative advantage against higher ranked programs is to know as much about applied empirical methods as I can. Data science has become extremely useful in economic research. The more comfortable I can get with large data sets and advanced empirical methods the better my work will be. From this class, my hope is to learn about a plethora of empirical methods that I can apply to future research. My interests in economics predominantly consist of labor and development. As of now I do not have an idea for a project, but I am actively thinking about what I should do. Ultimately, my goals for this class is to learn as much about data coding and applied data science methods to economics as I possibly can. My major hope in this class is to find a research idea that could turn into a part of my dissertation. Even if the class project is not something I wish to continue after the course, if my work on the project sparks further ideas I will feel like I moved forward in my studies. In the long run, my goal is to become an economics professor after graduation.

My current research interests involve Latin 
American development and socio-economic impacts of poverty in the U.S. I am hoping to come up with a good idea that involves first generation college students. I need to dive deeper into the relevant literature for such a topic. Throughout the PhD program I have had to focus predominantly on core examinations; however, now that I'm done with the exams, I have plenty of time to follow my passions. If a good teaching position does not present itself, I would also like to work for the Department of Labor or a think tank. I believe that as long as I am able to continue with research, and make decent money, I will be happy. 

\section{Equation}

\begin{equation}
    a^2+b^2=c^2
\end{equation}



\end{document}